### 2019-08-10 thesis.tex
*** empty log message ***

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this boundary, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics aims to understand the history, evolution, and physical behavior
of the most influential object in - and its impact on the dynamics of -
the space environment around our home planet.

% is not only
% a matter of scientific curiosity.
% Therefore, as a well established scientific discipline,
% solar and space physics aims to understand the history, evolution, and
% physical behavior of the most influential object in the space environment
% around our home planet.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{corona2017.png}
    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{figD2}
  \end{center}
\end{figure}

>>>>

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics can be summarized as to understand the history, evolution, and
physical processes of the most influential object in the space environment
around our home planet and its interaction with the solar system and the
interstellar medium.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{figD2}
  \end{center}
\end{figure}
